---
title: "assignment_1"
author: "Fang Liu"
date: "1/23/2022"
output: html_document
---

First, load in the required libraries. 
```{r, messages = FALSE}
library(tidyverse)
bc_data = read.csv("bcdata.csv")
```


### Question #1  
Construct a table providing summaries of the quantitative features of the dataset.Summaries should include the mean, median, minimum value, and maximum value.
```{r}
summary_data = summary(bc_data)
summary_data

```


### Question 2  
Recode BMI into the WHO-defined categories
```{r}
new_data = bc_data %>%
  mutate(
    BMI = case_when(
    BMI < 16.5 ~ "Severely underweight",
    BMI > 16.5 & BMI < 18.5 ~ "Underweight",
    BMI >= 18.5 & BMI <= 24.9 ~ "Normal weight",      
    BMI >= 25 & BMI <= 29.9 ~ "Overweight",
    BMI >= 30 & BMI <= 34.9 ~ "Obsesity class I",
    BMI >= 35 & BMI <=39.9 ~ "Obesity class II",
    TRUE ~ "Obesity class III")
    ) %>% 
  mutate(
    BMI = factor(BMI, levels = c("Severely underweight", "Underweight", "Normal weight", "Overweight", "Obsesity class I", "Obesity class II", "Obesity class III"))
  )
```


### Question 3
Create a bar chart showing the % of breast cancer cases and controls within each BMI category.

#### % of Breast Cancer 
```{r}
new_data2 =
new_data %>% 
  group_by(BMI) %>% 
  summarize(
    control = sum(Classification == 1) / n(),
    bc = sum(Classification == 2)/ n()
  ) %>% 
  ggplot(aes(x = BMI, y = bc, fill = BMI)) +
  geom_bar(stat = "identity")

new_data2
```

#### % of Control
```{r}
new_data3 =
new_data %>% 
  group_by(BMI) %>% 
  summarize(
    control = sum(Classification == 1) / n(),
    bc = sum(Classification == 2)/ n()
  ) %>% 
  ggplot(aes(x = BMI, y = control, fill = BMI)) +
  geom_bar(stat = "identity")

new_data3
```

### Question 4
```{r}

```


### Question 5
```{r}

```

